\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabto}
\renewcommand{\familydefault}{\sfdefault}
\begin{document}
\begin{center}
\thispagestyle{empty}
\LARGE \textbf{Rohit Rao\\}
\normalsize \href{mailto:rohitrao862@gmail.com}{rohitrao862@gmail.com} $\mid$ 609-865-7949 $\mid$ \href{https://github.com/rohitr02}{rohitr02}    \\
\hrulefill
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\noindent \textbf{\underline{OBJECTIVE}} \\
%\noindent Graduate student looking for domain positions starting month and year. \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\noindent \textbf{\underline{CORE SKILLS}} \\
%Skill 1 (years of experience), Skill 2 (years of experience), Skill 3 (years of experience) \\
% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Rutgers University -- New Brunswick} \hfill Piscataway, NJ \\
\textit{B.S. in Computer Science and Mathematics}  \hspace{1.40cm} GPA: 3.91/4.00 \hfill Sept, 2020 $-$ May, 2024
\begin{itemize}[noitemsep,nolistsep, leftmargin=*]
    \item {\textbf{Coursework -- Computer Science:} Intro to CS, Data Structures, Computer Architecture, Systems Programming}
    \item {\textbf{Coursework -- Mathematics:} Calculus 1, Calculus 2, Calculus 3 Honors, Intro to Linear Algebra, Intro to Math Reasoning Honors} \\
\end{itemize}
\textbf{WW-P High School South} \hfill West Windsor, NJ \\
\textit{High School Diploma} \hfill{GPA: 3.66/4.00} \hfill Sept, 2016 $-$ June, 2020 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentor and mentees for Android and iOS platform.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{RELEVANT EXPERIENCE}} \\
\noindent \textbf{Stria Labs} \hfill San Mateo, California \\
\textit{Firmware Intern} \hfill July, 2020 $-$ Sept, 2020
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Developed firmware in C++ that established communication between the Stria App and the hardware components of the Stria Band -- an assistive technology product for the blind to mitigate veering.}
\item {Developed a feature to read and process raw data from the hardware components and send it to the iPhone application via bluetooth.}
\item {Developed a feature to allow commands entered on the iPhone to interact with firmware and hardware -- specifically different commands could control certain code execution and enable/disable specific hardware components.}
\item {Worked with another firmware intern to develop a feature to allow commands to be sent from the hardware -- in the form of varying button presses -- to trigger actions on the iPhone application.}
\item {Collaborated with the mobile development interns to ensure that both the iPhone and hardware components were able to read/write data seamlessly.\\}
\end{itemize}

\noindent \textbf{Chinmaya Vrindavan Temple} \hfill Cranbury, NJ \\
\textit{Mobile App Developer} \hfill June, 2018 $-$ August, 2018
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Helped develop an application aimed to nurture the interest of Indian youth in their culture and religion.}
\item {Primarily responsible for developing the minigames that were the highlight of the application.}
\item {Contributed 4 different minigames in C\# using Unity3D to the larger application -- an endless runner, a card matching game, a flashcards game, and a gravity runner game.}
\item {Collaborated with a backend teammate to store and utilize media images from a server rather than storing them locally on the device.}
\item {Collaborated with the UI designer to integrate all 4 minigames into the larger application.}
\item {Volunteered over 100+ hours to the project.}\\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PERSONAL PROJECTS}} \\
\noindent \textbf{Artificially Intelligent Bots for a few Minigames -- Python}\hfill  April, 2020 $-$ June, 2020
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Developed several minigames including Flappy Bird, Snake, and an Endless Runner game in Python.}
\item {Created A.I. bots for each game that "evolved" and "learned" to play a game better over time.}
\item {Utilized the following libraries: Pygame, Neuro-Evolution of Augementing Technologies (NEAT), Numpy, Matplotlib, Pickle.}\\
\end{itemize}

\noindent \textbf{Genesis Calculator -- Swift} \hfill  July, 2019 $-$ August, 2019
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Developed an iOS application to calculate the minimum grades needed on future tests based on previous grades.}
\item {Created a feature to parse through text directly from Genesis (the grading platform) instead of manually entering grades.}\\
\end{itemize}

\noindent \textbf{Random Maze Generator Game -- Java} \hfill  Jan, 2018 $-$ March, 2018
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Developed a randomized solvable maze game that gets progressively more challenging as each maze is solved.}\\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{AWARDS AND CERTIFICATES}} \\
\noindent {Machine Learning for Business Professionals (Coursera)} \hfill June, 2020 \\
\noindent {Getting Started With AWS Machine Learning (Coursera)} \hfill May, 2020 \\
\noindent {Award at Hack TCNJ} \hfill February, 2019 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL SKILLS}} \\
\noindent \textbf{Programming Languages (Proficient):} Java, Python, Swift, C/C++, C\#\\
\end{document}
